Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Update todo
Study on multimodal data, update outlook of the field

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities. Also the rise of investigation into self-propelled cars and carpools. The study of energy efficient mobility is only in its emerging phase. \textbf{(Stojanovski, 2020)}

@@

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: read Biljecki
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering)
% TODO: Scientific study, disposition
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

@@

>>>>

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities.
Also the rise of investigation into self-propelled cars and carpools.
The study of energy efficient mobility such as walking and cycling is only in its emerging phase. \textbf{(Stojanovski, 2019)}

@@

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering, terrain (Procedural roads))
% TODO: Scientific study, disposition
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

@@

The fact is that much of the morpological information is not present in the OSM dataset.
Urban architects often work morpological structures where a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks 
All of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation.
But may even describe the building facades and distances between curbline and building lot.
\textbf{Stojanovski, 2019}
This type of information could in theory be generated procedurally using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.
